### 2015-12-31 fundamentals/impl.tex

\begin{align}
\min_{x} z &= \sum_{i\in I}\sum_{j\in J} c_{i,j}x_{i,j}& &\\
s.t & \sum_{i\in I_s}\sum_{j\in J} a_{i,j}^k x_{i,j} \le b_s^k & & \forall k\in K_s, \forall s\in S\\
    & \sum_{J\in J_r}\sum_{i\in I} a_{i,j}^k x_{i,j} \le b_r^k & & \forall k\in K_r, \forall r\in R\\
    & x_{i,j} \in [0,x_j] & & \forall i\in I, \forall j\in J
\end{align}
\begin{align}
\intertext{where}
S &= \mbox{suppliers}\nonumber\\
R &= \mbox{requesters}\nonumber\\
I_s &= \mbox{supply nodes for a supplier s}\nonumber\\
J_r &= \mbox{all request nodes for a requester r}\nonumber\\
K_s &= \mbox{constraints for a supplier s}\nonumber\\
K_r &= \mbox{constraints for a requester r}\nonumber\\
X &= \mbox{potential commodity flows}\nonumber\\
c_{i,j} &= \mbox{unit cost of flow from i to j}\nonumber\\
x_{i,j} &= \mbox{flow from node i to node j}\nonumber\\
a^k_{i,j} &= \mbox{constraint coeffiecient between i and j}\nonumber\\
b^k_s  &= \mbox{constraint k of supplier s}\nonumber\\
b^k_r &= \mbox{constraint k of requester r}\nonumber\\
\tilde{x}_j &= \mbox{requested quantity of request node j.}\nonumber
\end{align}

>>>>

\begin{align}
\min_{x} \: \: & z = c^\top x \\
\text{s.t.} \: \:  & A x \leq b \\
    & x_{i,j} \in [0, \tilde{x}_j] \: \:  \forall i \in I, \forall j \in J
\end{align}
\begin{align}
\intertext{where}
I &= \mbox{set of supply nodes}\nonumber\\
J &= \mbox{set of request nodes}\nonumber\\
c_{i,j} &= \mbox{unit cost of flow from i to j}\nonumber\\
x_{i,j} &= \mbox{flow from node i to node j}\nonumber\\
a^k_{i,j} &= \mbox{coefficient for constraint k between i and j}\nonumber\\
b^k_{s \mid r} &= \mbox{RHS for constraint k for a given supplier or requester}\nonumber\\
\tilde{x}_j &= \mbox{requested quantity of request node j.}\nonumber
\end{align}
